The \dealii Library, Version 9.2

### 2020-05-28 9.2/paper.tex
Reza added to the list of authors
Information about constexpr capabilities of dealii added

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item \dealii{} had decent support for solving complex-valued problems
  (e.g., ones in quantum mechanics -- like the example covered by the
  \texttt{step-58} tutorial program covered below -- or for
  time-harmonic problems) for a while already. However, there were two
  areas in which support was missing. First, the UMFPACK direct solver
  packaged with \dealii{} did not support solving complex-valued
  linear problems. This has now been addressed: UMFPACK actually can
  solve such systems, we just needed to write the appropriate
  interfaces. Second, the \texttt{DataOut} class that is responsible
  for converting nodal data into information that can then be written
  into files for visualization did not know how to deal with vector-
  and tensor-valued fields whose components are complex numbers. An
  example for this is to solve the time-harmonic version of the
  Maxwell equations that has the electric and magnetic fields as
  solution. This, too, has been addressed in this release.
  \item \todo[inline]{Reza: Please add a short summary of the
    \texttt{DiscreteTime} class}
\item z \todo[inline]{What else? Maybe mention the updated step-12?}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.

>>>>

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item \dealii{} had decent support for solving complex-valued problems
  (e.g., ones in quantum mechanics -- like the example covered by the
  \texttt{step-58} tutorial program covered below -- or for
  time-harmonic problems) for a while already. However, there were two
  areas in which support was missing. First, the UMFPACK direct solver
  packaged with \dealii{} did not support solving complex-valued
  linear problems. This has now been addressed: UMFPACK actually can
  solve such systems, we just needed to write the appropriate
  interfaces. Second, the \texttt{DataOut} class that is responsible
  for converting nodal data into information that can then be written
  into files for visualization did not know how to deal with vector-
  and tensor-valued fields whose components are complex numbers. An
  example for this is to solve the time-harmonic version of the
  Maxwell equations that has the electric and magnetic fields as
  solution. This, too, has been addressed in this release.
  \item \todo[inline]{Reza: Please add a short summary of the
    \texttt{DiscreteTime} class}
\item Certain types of quantities in a simulation are constants fully known
  at compile time. They can be pre-calculated and fully stored inside the
  compiled program binary in order to avoid unnecessary initialization during
  runtime. This optimization is now enabled for the class templates
  \texttt{Tensor} and \texttt{SymmetricTensor} by qualifying their constructor,
  member functions, and overloaded operators as \texttt{constexpr}.
  For instance, the linear mechanical constitutive model for elastic solids
  uses a constant fourth-order elasticity tensor
  $\mathbb{C} = \lambda \boldsymbol{I} \otimes \boldsymbol{I} + 2 \mu \mathbb{I}$
  which does not depend on the current state of strain.
  This tensor can be statically initialized by defining it as
  \texttt{constexpr SymmetricTensor<4, dim>}.
  As another example, the lattice vectors in a crystal plasticity model are generally
  constant and known during compilation time, enabling their efficient definition as
  \texttt{constexpr Tensor<1, dim>}.
\item z \todo[inline]{What else? Maybe mention the updated step-12?}
\end{itemize}
%
In addition to these changes, the changelog lists more than 200 other
features and bugfixes.
